---
title: "workout01-maiah-johnson"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, fig.path = '/users/maiahjohnson/stat133/workout1/report')
```


```{r}
sal_g <- ggplot(data = teams, aes(x = team, y = total_salary/1000000)) + geom_bar(stat = 'identity') + coord_flip()
sal_g + labs(title = "NBA Teams Ranked by Total Salary", y = "Salary(in millions", x = "Team") + geom_hline(yintercept = 75)
point_g <- ggplot(data = teams, aes(x = team, y = total_points)) + geom_bar(stat = 'identity') + coord_flip()
point_g + labs(title = "NBA Teams Ranked by Total Points", y = "Points", x = "Team") + geom_hline(yintercept = 4000)
eff_g <- ggplot(data = teams, aes(x = team, y = total_eff)) + geom_bar(stat = 'identity') + coord_flip()
eff_g + labs(title = "NBA Teams Ranked by Total Efficiency", y = "Efficiency", x = "Team") + geom_hline(yintercept = 85)
block_g <- ggplot(data = teams, aes(x = team, y = total_blocks)) + geom_bar(stat = 'identity') + coord_flip()
block_g + labs(title = "NBA Teams Ranked by Total Blocks", y = "Blocks", x = "Team") + geom_hline(yintercept = 0)

```

###Comments and Reflections 
I found it dfficult to put all of the componenets we've used together on this larger assignment. Given that we needed alot of the knowledge from lab06 to complete this I wish we would have been exposed to that lab earlier. I am still unsure of how to properly order the bars for the geom_bar function. I tried various formats but still had difficulty. The R script is just a giant code chunk, but before I relized this I was unsure of how to create code within it. 